Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/2.GenericProgramming.tex
Language edits, caption edits

@@

\begin{figure}
\begin{Verbatim}[frame=leftline]
# pragma model parallel for simd vectorize tile unroll fuse
for ( size_t i = 0; i < N; ++i) {
 /* loop body */
}
\end{Verbatim}
\caption{Declarative parallel programming provides uses pragma annotations to capture semantic information.}
\label{figOMPLike}
\end{figure}

\begin{figure}
\begin{Verbatim}[frame=leftline]
model::parallel_for (N, [=] ( const size_t i) {
  /* loop body */
});
\end{Verbatim}
\caption{Imperative parallel programming uses a base language and relies on programming interfaces to capture information and a documentation that describe their semantics.}
\label{figKokkosLike}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.45\textwidth]{img/Hollman.png}}
\caption{The Hollman pic :) - placeholder}
\label{fig}
\end{figure}

@@

\begin{figure}
\begin{Verbatim}[frame=leftline]
# pragma model parallel for simd vectorize tile unroll fuse
for ( size_t i = 0; i < N; ++i) {
 /* loop body */
}
\end{Verbatim}
\caption{Imperative model tells the compiler to use simd and vectorize and tile and unroll and fuse. It lists specific optimizations that should be made}
\label{figOMPLike}
\end{figure}

\begin{figure}
\begin{Verbatim}[frame=leftline]
model::parallel_for (N, [=] ( const size_t i) {
  /* loop body */
});
\end{Verbatim}
\caption{Declarative model expresses parallelism and relies on the model to map it effectively to the architecture}
\label{figKokkosLike}
\end{figure}
